On The Benefits of Magnitude Estimation Relevance Assessments for Information Retrieval Evaluation

### 2016-09-28 0_abstract.tex
Final camera ready version

Magnitude estimation is a psychophysical scaling technique for the
measurement of sensation, where observers assign numbers to stimuli in
response to their perceived intensity.
We investigate the use of magnitude estimation for judging the
relevance of documents for information retrieval
evaluation, carrying out a large-scale user study across 18 TREC topics
and collecting
over 50,000 magnitude estimation judgments using crowdsourcing.
%
Our analysis shows that magnitude estimation judgments 
\textcolor{red}{ can be
reliably collected using crowdsourcing,  are competitive in terms of
assessor cost, and} are, on average, 
rank-aligned with ordinal judgments made by expert relevance assessors.

>>>>

Magnitude estimation is a psychophysical scaling technique for the
measurement of sensation, where observers assign numbers to stimuli in
response to their perceived intensity.
We investigate the use of magnitude estimation for judging the
relevance of documents for information retrieval
evaluation, carrying out a large-scale user study across 18 TREC topics
and collecting
over 50,000 magnitude estimation judgments using crowdsourcing.
%
Our analysis shows that magnitude estimation judgments 
can be
reliably collected using crowdsourcing,  are competitive in terms of
assessor cost, and are, on average, 
rank-aligned with ordinal judgments made by expert relevance assessors.

### 2016-09-28 2_bg.tex
Final camera ready version

\textcolor{red}{ This paper is a revised and extended version of
research that appeared at SIGIR 2015~\cite{ME-SIGIR15}.
In particular, this version adds: a new research question of whether
crowdsourcing is a viable method to gather robust magnitude estimation
values (RQ2); related background on crowdsourcing; more information on
the ME score distributions reported in Section~\ref{sec:descr-stat},
including Figures~\ref{fig:ME-raw-scores} and~\ref{fig:ME-norm-scores}
and their discussion; a new Section~\ref{sec:cs} including
Figure~\ref{fig:judgeVariability} and re-computation of
Figure~\ref{fig:workersQuality}; new material in Section~\ref{sec:rq2},
including re-computation of Figures~\ref{fig:runs-rerank-median3best}
and~\ref{fig:runs-rerank-median3best-fake}; a revised second half of
Section~\ref{sec-rq3}; an Appendix giving exact participant
instructions; and additional references.
}

@@

\textcolor{red}{However, it is important to note that disagreement does
not necessarily imply low worker quality.
As pointed out for example by \citet{aroyo2015truth}, disagreement
might depend on the false assumption of a ``unique truth'', it might
carry useful information that can be exploited, and attempts to
eliminate disagreement, for example by detailed instructions, might not
improve quality and simply lead to information loss.}

>>>>

This paper is a revised and extended version of
research that appeared at SIGIR 2015~\cite{ME-SIGIR15}.
In particular, this version adds: a new research question of whether
crowdsourcing is a viable method to gather robust magnitude estimation
values (RQ2); related background on crowdsourcing; more information on
the ME score distributions reported in Section~\ref{sec:descr-stat},
including Figures~\ref{fig:ME-raw-scores} and~\ref{fig:ME-norm-scores}
and their discussion; a new Section~\ref{sec:cs} including
Figure~\ref{fig:judgeVariability} and re-computation of
Figure~\ref{fig:workersQuality}; new material in Section~\ref{sec:rq2},
including re-computation of Figures~\ref{fig:runs-rerank-median3best}
and~\ref{fig:runs-rerank-median3best-fake}; a revised second half of
Section~\ref{sec-rq3}; an Appendix giving exact participant
instructions; and additional references.

@@

However, it is important to note that disagreement does
not necessarily imply low worker quality.
As pointed out for example by \citet{aroyo2015truth}, disagreement
might depend on the false assumption of a ``unique truth'', it might
carry useful information that can be exploited, and attempts to
eliminate disagreement, for example by detailed instructions, might not
improve quality and simply lead to information loss.

### 2016-09-28 4_descriptive_stats.tex
Final camera ready version

\textcolor{red}{
Given that the  scores for document relevance that we have observed are 
distributed as seen previously in other tasks where magnitude estimation has been used, 
we can adopt normalizing and aggregating approaches that have been used before in
the literature.
}

>>>>

Given that the scores for document relevance that we
have observed are distributed similarly to other tasks where magnitude
estimation has been used, we can proceed to adopt normalizing and
aggregating approaches that have been used previously in the literature, as
explained in the next section.

### 2016-09-28 6_results_RQ2.tex
Final camera ready version

In our data, there are
at least ten workers judging the same topic-document pair, and
the source of internal disagreement might be threefold:
(i) the arbitrary, personal scale used by a judge when expressing an ME
score; 
(ii) the subjective nature of relevance; and 
(iii) the often-feared low quality of work in crowdsourcing exercises.
The first has already been discussed and is removed by the geometric
average normalization process (Section~\ref{sec:score-normalization}).
The second is a feature that one might not want to remove from the
data: different judges can truly have different opinions on the
relevance of a document, whatever scale of measurement is used.
Usually IR evaluators assume that this variation is distilled into a single 
value (for example: mean, median or mode) 
that represents a population of users \textcolor{red}{(although there might in fact not be a unique truth~\citep{aroyo2015truth})}.
Of course, the third source is in need of particular attention: low
quality workers might express unreliable scores, and in general this
would lead to low internal agreement.

@@

\textcolor{red}{While this argument is far from being conclusive, it
confirms that the ten workers that we used in our experiment, and the
associated cost, can be reduced.
Therefore, from the about $\$0.4$ for each document figure mentioned in
Section~\ref{sec:crowd-judging} we can estimate that only about $\$0.3$
for each document are really needed, if not less since more efficient
methods could be devised.}

@@

\textcolor{red}{ 
Using ME with crowdsourcing could potentially raise
several concerns, including: 
subjectiveness of the relevance scale; 
difficulty in normalizing disparate scales from different workers; 
lack of proper training of workers;
potential internal and/or external disagreement between workers;
and high overall cost as redundant workers needed to ensure quality.
On the basis of the results presented so far we can conclude that, at
least with our setting and our quality checks in place (see items
(a)--(d) in Section~\ref{sec:quality-checks}), we can be reassured that
magnitude estimation relevance scores gathered by means of
crowdsourcing are reliable, thus answering RQ\ref{item:rq4}.
Also, the cost to collect the ME judgments in our experiments 
is comparable to that of collecting ordinal scale judgments, 
and there are hints that this cost can be lowered by collecting fewer judgments.
}

>>>>

In our data, there are
at least ten workers judging the same topic-document pair, and
the source of internal disagreement might be threefold:
(i) the arbitrary, personal scale used by a judge when expressing an ME
score; 
(ii) the subjective nature of relevance; and 
(iii) the often-feared low quality of work in crowdsourcing exercises.
The first has already been discussed and is removed by the geometric
average normalization process (Section~\ref{sec:score-normalization}).
The second is a feature that one might not want to remove from the
data: different judges can truly have different opinions on the
relevance of a document, whatever scale of measurement is used.
Usually IR evaluators assume that this variation is distilled into a single 
value (for example: mean, median or mode) 
that represents a population of users (although there might in fact not be a unique truth~\citep{aroyo2015truth}).
Of course, the third source is in need of particular attention: low
quality workers might express unreliable scores, and in general this
would lead to low internal agreement.

@@

While this argument is far from being conclusive, it
confirms that the ten workers that we used in our experiment, and the
associated cost, can be reduced.
Therefore, from the about $\$0.4$ for each document figure mentioned in
Section~\ref{sec:crowd-judging} we can estimate that only about $\$0.3$
for each document are really needed, if not less since more efficient
methods could be devised.

@@

Using ME with crowdsourcing could potentially raise
several concerns, including: 
subjectiveness of the relevance scale; 
difficulty in normalizing disparate scales from different workers; 
lack of proper training of workers;
potential internal and/or external disagreement between workers;
and high overall cost as redundant workers needed to ensure quality.
On the basis of the results presented so far we can conclude that, at
least with our setting and our quality checks in place (see items
(a)--(d) in Section~\ref{sec:quality-checks}), we can be reassured that
magnitude estimation relevance scores gathered by means of
crowdsourcing are reliable, thus answering RQ\ref{item:rq4}.
Also, the cost to collect the ME judgments in our experiments 
is comparable to that of collecting ordinal scale judgments, 
and there are hints that this cost can be lowered by collecting fewer judgments.

### 2016-09-28 7_results_RQ3.tex
Final camera ready version

Rather than simply taking the median of all ME scores assigned to a
document, we take the median of scores taken from the three units that
have document orderings that have the highest agreement with the TREC
orderings, or Sormunen orderings, respectively.
In effect, the scores derived from units with high internal agreement
as computed in Section~\ref{sec:internal-agreement}, with ties broken
in favor of units with the least unjudged documents.
By aggregating scores over units that have a high agreement with the
original TREC orderings, any differences in system rankings we see
should be more attributable to the scale of the gain values, rather
than perturbations in document orderings given by different gain
values.
\textcolor{red}{Note that this is a slightly less confounded methodology 
than was used in our previous paper~\cite{ME-SIGIR15}, which simply
took the median of all units, even if the unit wildly disagreed with
the ordering of documents given by the categorical judgments.
This revised methodology accounts for the differences between the
figures and tables in this section and in the previous paper.}

@@

\textcolor{red}{ Generally the correlations between the system rankings
based on categorical and ME gain values are higher when the wide
judgments are used as opposed to the narrow judgments.
This contradicts our expectations from Table~\ref{tab:scaling-cats},
which indicated that a larger scale of gains led to a decrease in
correlations.
This confirms that a simple argument based on the scale of judgments is
not sufficient to explain the different system orderings, although the
number of topics used here is small (12).
We examine this further in the next section.
}

@@

\textcolor{red}{ In answering RQ\ref{item:rq2}, we have shown that
there are clear differences in system rankings using nDCG and ERR
metrics on this data when using ME scores as gain values compared with
using ordinal categories as gain values.
Depending on the judgments and the metric used, correlations between
system orderings using ME and the categorical judgments, as measured
with Kendall's $\tau$, varied between about 0.8 and -0.2. At first this
might seem like a simple scaling problem, where ME judgments are over
a wider range than categorical judgments.
However, analysis shows that simple factor cannot be the whole answer;
a much more likely explanation is that there is substantial individual
variance in not only how people perceive the relevance of an individual
document, but also in how they perceive the ratio of relevance of one
document to another.
}

>>>>

Rather than simply taking the median of all ME scores assigned to a
document, we take the median of scores taken from the three units that
have document orderings that have the highest agreement with the TREC
orderings, or Sormunen orderings, respectively.
In effect, the scores derived from units with high internal agreement
as computed in Section~\ref{sec:internal-agreement}, with ties broken
in favor of units with the least unjudged documents.
By aggregating scores over units that have a high agreement with the
original TREC orderings, any differences in system rankings we see
should be more attributable to the scale of the gain values, rather
than perturbations in document orderings given by different gain
values.
Note that this is a slightly less confounded methodology 
than was used in our previous paper~\cite{ME-SIGIR15}, which simply
took the median of all units, even if the unit wildly disagreed with
the ordering of documents given by the categorical judgments.
This revised methodology accounts for the differences between the
figures and tables in this section and in the previous paper.

@@

Generally the correlations between the system rankings
based on categorical and ME gain values are higher when the wide
judgments are used as opposed to the narrow judgments.
This contradicts our expectations from Table~\ref{tab:scaling-cats},
which indicated that a larger scale of gains led to a decrease in
correlations.
This confirms that a simple argument based on the scale of judgments is
not sufficient to explain the different system orderings, although the
number of topics used here is small (12).
We examine this further in the next section.

@@

In answering RQ\ref{item:rq2}, we have shown that
there are clear differences in system rankings using nDCG and ERR
metrics on this data when using ME scores as gain values compared with
using ordinal categories as gain values.
Depending on the judgments and the metric used, correlations between
system orderings using ME and the categorical judgments, as measured
with Kendall's $\tau$, varied between about 0.8 and -0.2. At first this
might seem like a simple scaling problem, where ME judgments are over
a wider range than categorical judgments.
However, analysis shows that simple factor cannot be the whole answer;
a much more likely explanation is that there is substantial individual
variance in not only how people perceive the relevance of an individual
document, but also in how they perceive the ratio of relevance of one
document to another.

### 2016-09-28 8_results_RQ4.tex
Final camera ready version

\textcolor{red}{ In the previous section, and in this section, we have
seen not only that relevance values for a single document vary among
users, but the ratio of relevance between two documents also varies.
Thus, in answer to RQ\ref{item:rq3}, the selection of a single gain
formulation as either a linear or exponential mapping of categorical
judgments is guaranteed to misrepresent at least half of our users in
this data set.
Similarly, choosing a single gain formulation to maximize the
statistical efficiency of system comparisons will also misrepresent a
large part of the user population.
}

>>>>

In the previous section, and in this section, we have
seen not only that relevance values for a single document vary among
users, but the ratio of relevance between two documents also varies.
Thus, in answer to RQ\ref{item:rq3}, the selection of a single gain
formulation as either a linear or exponential mapping of categorical
judgments is guaranteed to misrepresent at least half of our users in
this data set.
Similarly, choosing a single gain formulation to maximize the
statistical efficiency of system comparisons will also misrepresent a
large part of the user population.
